---
title: "Worksheet: EDA Worksheet"
subtitle: "STT 2860 Intro to Data Mgmt & Visualization" 
author: "PUT YOUR NAME HERE"
date: "`r format(Sys.time(), '%A, %B %d, %Y @ %I:%M %p')`"
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4 
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

### Packages Used

```{r}
# load all packages used here
library(tidyverse)
library(tidyverse)
library(nycflights13)
library(skimr)

```


### Datasets Used

#### Popular Kids

The dataset `popular.csv` and you can read about it [HERE](https://stat-jet-asu.github.io/Datasets/InstructorDescriptions/popular.html).

```{r}
# import the dataset from the web URL
kids <- read_csv("https://aokine.github.io/Data/popular.csv")
```

```{r}
# explore the dataset

```



#### Semmelweis Data

The dataset `semmelweisannualbyclinic.csv` and you can read about Dr. Ignaz Semmelweis [HERE](https://www.pbs.org/newshour/health/ignaz-semmelweis-doctor-prescribed-hand-washing). This dataset contains annual observations for two different clinics that led him to implement his handwashing experiment.

```{r}
semm <- read_csv("https://aokine.github.io/Data/semmelweisannualbyclinic.csv")
```

```{r}
# explore the dataset
```


### NFL PLayers 2016 Dataset

Description: https://stat-jet-asu.github.io/Datasets/InstructorDescriptions/NFLplayers2016.html

#### Load the dataset

```{r}
NFL <- read_csv("https://aokine.github.io/Data/NFLplayers2016.csv")
```

#### Explore the structure with `skim()`

```{r}

```

### Barplots with `geom_bar()`

For `geom_bar()`, we input an `x` variable and the geometry counts how many of each value occurs in that variable, and that become the "y" value for the height of the bars. Use `x=PositionGrp`


```{r}

```



## Fixing category names include: Map `PositionGrp` to the y aesthetic

```{r}

```



## Barplot for Two Variables

Use `PositionGrp` and `Side` as the two variables. Allow colors of bars to change using a variable. 

```{r}

```




### Barplots with `geom_col()`

For `geom_col()`, we input an `x` variable and we input a `y` variable that specifies the heights of the bars. The data is already summarized somehow.

I can count the categories up myself to generate a smaller dataset with categories and counts. I get a dataset with two variables: the variable I counted, and one called `n` that is the counts.

```{r}

```

```{r}

```


## Rearrange the bars in order using the `reorder()` function. 

Change the order of the categories according to their counts.

```{r}

```




### Facets

#### Facet Wrap

Create a basic Histogram using `Weight`

```{r}

```

Create a Histogram with Fill using `PositionGrp` or `Side`

```{r}

```


Create a Histogram Using `facet_wrap()` with `PositionGrp` variable

```{r}

```


Create a Histogram Using `facet_grid()` with `Side` variable

```{r}

```



***
```{r}
sessionInfo()
```